---
title: "Vince's Quarto Shiny Document"
format: html
server: shiny
---

## App Tabs

::::: panel-tabset
### Basic quarto operations

## Structured narrative with emphases and proper orthography

I use simple markup to **emphasize** or *focus attention on* specific words or phrases.

I can add HTML "in line" to achieve <u>underlining</u>.

#### Lower-level heading 1

#### Lower-level heading 2

#### Orthography with markdown

`caf&eacute` renders to caf&eacute;,  `Cura&ccedil;ao` renders to Cura&ccedil;ao

#### Orthography with unicode

Specific unicode characters have `\u` as prefix for rendering via inline R.  \\u5f20 and \\uae40 render as:

`r "\u5f20"`, `r "\uae40"`

#### Mathematical annotation with embedded code and graphics

We looked at
$$f(x) = ax^2 + bx + c = 0$$

We can program the function in R as
```{r lkf1, echo=TRUE}
f = function(x, a, b, c) a*x^2 + b*x + c
```
and evaluate it:
```{r lkf2, echo=TRUE}
f(3, 1, 1, 1)
```
Define a domain of evaluation:
```{r lkf3, echo=TRUE}
dom = seq(-5, 5, .5)
```
Obtain values for specific coefficient settings:
```{r lkf4, echo=TRUE}
vals = f(dom, 1, -1, -2)
```
Use base R graphics to display:
```{r lkf5, echo=TRUE}
plot(dom, vals)
```

### Interactive viz

Using ggplot2 and plotly, we can support
tooltips to get information about specific
point.
```{r lkf6, echo=TRUE, message=FALSE}
library(ggplot2)
library(plotly)
p1 = ggplot(mapping=aes(x=dom, y=vals)) + geom_point()
ggplotly(p1)
```
### Interactive tables

```{r lktab, echo=TRUE, message=FALSE}
library(DT)
datatable(iris)
```

### App

::: panel-sidebar
```{r}
helpText("This is a simple app in quarto.")
sliderInput("obs", "Number of observations:", min = 10, max = 500, value = 100)
```
:::

::: panel-fill
```{r}
plotOutput("distPlot")
```
:::

### About

This quarto document demonstrates 

- literate programming, with code narrated and executed
- interactive visualization of data with plotly
- interactive table display with DT
- a simple Quarto + Shiny app that draws a histogram from random normal values. 
:::::

```{r}
#| context: server
output$distPlot <- renderPlot({
  hist(rnorm(input$obs))
})
```
