---
title: "My Quarto Shiny Document"
format: html
server: shiny
---

## App Tabs

::: {.panel-tabset}

### Basic quarto operations

## Structured narrative with emphases and proper orthography

I use simple markup to **emphasize** or _focus attention on_ specific words or phrases.

I can add HTML "in line" to achieve <u>underlining</u>.

#### Lower-level heading 1

#### Lower-level heading 2

#### Mathematical annotation with embedded code

We looked at 
$$
f(x) = ax^2 + bx + c = 0
$$


### App

::: {.panel-sidebar}
```{r}
helpText("This is a simple app in quarto.")
sliderInput("obs", "Number of observations:", min = 10, max = 500, value = 100)
```
:::

::: {.panel-fill}
```{r}
plotOutput("distPlot")
```
:::

### About

This tab demonstrates a simple Quarto + Shiny app that draws a histogram from random normal values.
Use the slider in the **App** tab to change the number of observations.

:::

```{r}
#| context: server
output$distPlot <- renderPlot({
  hist(rnorm(input$obs))
})
```

